Summary Tables

### 2021-01-13 summary_tables.Rmd
Update propensities

|accra|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 95.6|37.9|2.5 |
| cycle | 0.6|0.9|0.3 |
| car | 3.2|18.1|10.0 |
| motorcycle | 0.0|0.1|1.1 |
| bus | 0.0|29.7|80.5 |

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 75.0|23.1|1.0 |
| cycle | 2.3|9.8|1.2 |
| car | 1.0|4.3|6.4 |
| motorcycle | 5.1|33.9|63.2 |
| bus | 15.1|24.3|24.9 |

@@

|bogota|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 80.8|11.1|1.0 |
| cycle | 7.9|11.7|2.1 |
| car | 3.2|18.9|17.7 |
| motorcycle | 1.4|8.0|6.4 |
| bus | 4.9|43.2|70.1 |

@@

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 90.2|7.4|0.1 |
| cycle | 3.3|4.6|0.3 |
| car | 2.1|33.1|30.2 |
| motorcycle | 0.6|4.5|1.1 |
| bus | 1.6|37.0|49.1 |

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 83.9|4.0|0.1 |
| cycle | 6.4|6.3|0.4 |
| car | 7.5|54.7|29.8 |
| motorcycle | 0.2|1.8|0.9 |
| bus | 0.6|21.2|30.3 |

>>>>

|accra|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 95.5|27.9|2.6 |
| cycle | 0.6|0.7|0.4 |
| car | 0.9|12.4|17.2 |
| motorcycle | 0.0|0.0|1.3 |
| bus | 2.4|48.3|71.8 |

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 74.9|23.0|1.0 |
| cycle | 2.3|9.8|1.2 |
| car | 1.0|4.4|6.4 |
| motorcycle | 5.1|33.9|63.2 |
| bus | 15.1|24.4|25.0 |

@@

|bogota|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 80.5|10.7|1.0 |
| cycle | 7.9|11.3|2.0 |
| car | 3.5|21.6|19.7 |
| motorcycle | 1.4|7.7|6.2 |
| bus | 4.9|41.6|68.3 |

@@

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 89.6|6.5|0.1 |
| cycle | 3.4|4.5|0.3 |
| car | 2.2|34.9|29.7 |
| motorcycle | 0.6|4.7|1.0 |
| bus | 1.6|36.2|49.9 |

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 83.9|4.1|0.1 |
| cycle | 6.2|6.0|0.4 |
| car | 7.7|54.8|30.0 |
| motorcycle | 0.2|2.0|0.9 |
| bus | 0.6|21.1|30.1 |
